Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-12-04 astronum_2017/astronum-amrex.tex
fix some typos

Among the most significant open questions for SNe Ia is the identity of the
progenitor.  About 20 years ago, the community had
mostly converged upon the single-degenerate scenario---a
Chandrasekhar-mass C/O white dwarf that accretes from its companion,
eventually leading to runaway at the center that burns through the
star (see~\cite{hillebrandtniemeyer2000} for the state of the field at
that time).  Since then, a wealth of observations has indicated that
there is a lot of diversity in SNe Ia, and searches for progenitor
systems have strongly suggested that Chandra-mass white dwarfs cannot
explain most SNe Ia.  Today, merging white dwarfs (the double
degenerate scenario) has perhaps become the most popular model.
Other progenitors, like He burning on the surface of a sub-Chandra
white dwarf, have also seen interest in explaining some of the observed
diversity.  See~\cite{araa-maoz} for a review.

@@

Figure~\ref{fig:knl-gpu-scaling} shows the performance of
\starlord\ on the Summitdev platform at OLCF\footnote{Summitdev
  consists of 2 IBM Power8 processors and 4 NVIDIA Pascal GPUs per
  node.}.  The highest GPU count (128) corresponds to 32 nodes on
Summitdev.  We see a nearly linear speedup with the number of GPUs,
indicating good weak scaling on this machine. A single P100 GPU achieves
a performance approximately 2.5 times that of the 20 Power8 cores. Efforts are underway to
complete the port of the GPU developments into \castro.  This figure
also shows our performance on the Intel Xeon Phi manycore processors (using
NERSC Cori).  This is for the same problem as the self-gravity test on
Titan.  The Intel Xeon Phi chips in Cori
have 68 cores than can be run with 1, 2, or 4 hardware threads each.
For all these runs, we ran with 4 threads / core (272
threads / chip).  We have not yet focused on optimizing \castro\ for the
Intel Xeon Phi architecture.

>>>>

Among the most significant open questions for SNe Ia is the identity of the
progenitor.  About 20 years ago, the community had
mostly converged upon the single-degenerate scenario---a
Chandrasekhar-mass C/O white dwarf that accretes from its companion,
eventually leading to runaway at the center that burns through the
star (see~\cite{hillebrandtniemeyer2000} for the state of the field at
that time).  Since then, a wealth of observations has indicated that
there is a lot of diversity in SNe Ia, and searches for progenitor
systems have strongly suggested that Chandra-mass white dwarfs cannot
explain most SNe Ia.  Today, a pair of merging white dwarfs (the double
degenerate scenario) has perhaps become the most popular model.
Other progenitors, like He burning on the surface of a sub-Chandra
white dwarf, have also seen interest in explaining some of the observed
diversity.  See~\cite{araa-maoz} for a review.

@@

Figure~\ref{fig:knl-gpu-scaling} shows the performance of
\starlord\ on the Summitdev platform at OLCF\footnote{Summitdev
  consists of 2 IBM Power8 processors and 4 NVIDIA Pascal GPUs per
  node.}.  The highest GPU count (128) corresponds to 32 nodes on
Summitdev.  We see a nearly linear speedup with the number of GPUs,
indicating good weak scaling on this machine. A single P100 GPU achieves
a performance approximately 2.5 times that of the 20 Power8 cores. Efforts are underway to
complete the port of the GPU developments into \castro.  This figure
also shows our performance on the Intel Xeon Phi manycore processors (using
NERSC Cori).  This is for the same problem as the self-gravity test on
Titan.  The Intel Xeon Phi chips in Cori
have 68 cores that can be run with 1, 2, or 4 hardware threads each.
For all these runs, we ran with 4 threads / core (272
threads / chip).  We have not yet focused on optimizing \castro\ for the
Intel Xeon Phi architecture.
